Hierarchical Time Series Forecasting in Emergency Medical Services

### 2023-07-19 manuscript/02-literature.qmd
Minor rewording, typos and fixed some refs

@sasaki2010using develop a multivariable regression model to estimate future EMS demands. In addition to the historical demand, the population census for different age groups and counts of the number of companies employing more than five people are included in the regression. The census variables describe groups who are more likely to need an ambulance. A stepwise ordinary least squares regression analysis is used for estimating the parameter and generating forecasts. The only performance measure reported in this study is $R^2$, which is not an effective measure of forecast accuracy [@armstrong01, p457]. The research design of this study is not rigorous and the study is not reproducible. @vile2012predicting explore using a Singular Spectrum Analysis (SSA) method to generate forecasts of the EMS demand at the national level for 7-day, 14-day, 21-day, and 28-day forecast horizons using data provided by an ambulance service in Great Britain. The performance of this approach is compared to Auto-Regressive Integrated Moving Average (ARIMA) and Holt-Winters time series methods using Root Mean Squared Error (RMSE). They concluded that point forecasts generated by SSA are more accurate for longer-term, but that ARIMA and Holt-Winters performance is superior for shorter-term horizons. @vile2016time further develop a decision support system to integrate forecasts generated by SSA. However, the study does not compare and contrast the performance of forecasting methods based on utility measures such as cost, resource utilization and response time. The tool contains options that allow generating forecasts at various levels of granularity; however, it ignores the structure of the hierarchical and grouped relationships, preventing aligned decision making and coordination. @al2021empirical \textcolor{teal}{utilises real data from the Welsh Ambulance Service to explore the forecast accuracy of four forecasting approaches: ARIMA, Holt Winters, Multiple Regression, and Singular Spectrum Analysis (SSA) in predicting call volume demand accurately. The aim is to compare these approaches with the current method across various planning horizons (7 days, 30 days, and 90 days) for both total call volume and category-specific demand. Forecast accuracy performance is evaluated using root mean square error (RMSE) and mean absolute percentage error (MAPE) are calculated. The findings indicate that ARIMA performs the best in predicting weekly and monthly demand. However, when it comes to long-term demand, the SSA method proves to be the most effective.} @ibrahim2016modeling \textcolor{teal}{conducted a case study to assess the effectiveness of multiple forecasting methods: the multiplicative univariate forecasting model (MU), univariate mixed-effects model (ME), bivariate mixed-effects model (BME1), and bivariate mixed-effects model (BME2). Real-life call centre data was utilised to forecast for periods of 1, 7, and 14 days ahead, using only a limited dataset of 42 days. The performance of these forecasting methods was evaluated using two metrics: RMSE for point forecasts and coverage probability for the 95\% prediction interval. The findings indicate that the ME consistently produces the most accurate point forecasts. On the other hand, BME1 and BME2 demonstrate superior coverage probabilities when forecasting for one day or one week ahead. For a two-week leading period, MU shows better coverage probability.}

>>>>

@sasaki2010using develop a multivariable regression model to estimate future EMS demands. In addition to the historical demand, the population census for different age groups and counts of the number of companies employing more than five people are included in the regression. The census variables describe groups who are more likely to need an ambulance. A stepwise ordinary least squares regression analysis is used for estimating the parameter and generating forecasts. The only performance measure reported in this study is $R^2$, which is not an effective measure of forecast accuracy [@armstrong01, p457]. The research design of this study is not rigorous and the study is not reproducible. @vile2012predicting explore using a Singular Spectrum Analysis (SSA) method to generate forecasts of the EMS demand at the national level for 7-day, 14-day, 21-day, and 28-day forecast horizons using data provided by an ambulance service in Great Britain. The performance of this approach is compared to Auto-Regressive Integrated Moving Average (ARIMA) and Holt-Winters time series methods using Root Mean Squared Error (RMSE). They concluded that point forecasts generated by SSA are more accurate for longer-term, but that ARIMA and Holt-Winters performance is superior for shorter-term horizons. @vile2016time further develop a decision support system to integrate forecasts generated by SSA. However, the study does not compare and contrast the performance of forecasting methods based on utility measures such as cost, resource utilization and response time. The tool contains options that allow generating forecasts at various levels of granularity; however, it ignores the structure of the hierarchical and grouped relationships, preventing aligned decision making and coordination. @al2021empirical \textcolor{teal}{utilises data from the Welsh Ambulance Service to explore the forecast accuracy of four forecasting approaches: ARIMA, Holt Winters, Multiple Regression, and Singular Spectrum Analysis (SSA) in predicting call volume demand. The aim is to compare these approaches with the current method across various planning horizons (7 days, 30 days, and 90 days) for both total call volume and category-specific demand. Forecast accuracy performance is evaluated using root mean square error (RMSE) and mean absolute percentage error (MAPE). The findings indicate that ARIMA performs the best in predicting weekly and monthly demand. However, when it comes to long-term demand, the SSA method proves to be the most effective.} @ibrahim2016modeling \textcolor{teal}{conducted a case study to assess the effectiveness of multiple forecasting methods: the multiplicative univariate forecasting model (MU), univariate mixed-effects model (ME), bivariate mixed-effects model (BME1), and bivariate mixed-effects model (BME2). Call centre data were utilised to forecast for periods of 1, 7, and 14 days ahead, using only a limited dataset of 42 days. The performance of these forecasting methods was evaluated using two metrics: RMSE for point forecasts and coverage probability for the 95\% prediction interval. The findings indicate that the ME consistently produces the most accurate point forecasts. On the other hand, BME1 and BME2 demonstrate superior coverage probabilities when forecasting for one day or one week ahead. For a two-week leading period, MU shows better coverage probability.}

### 2023-07-19 manuscript/03-experiment.qmd
Minor rewording, typos and fixed some refs

\textcolor{teal}{In this paper, the strength of trend and seasonality were calculated using the "STL" (Seasonal and Trend decomposition using Loess) decomposition method, as described by} @kang2017visualising. \textcolor{teal}{STL is a widely used and flexible method for decomposing time series data into trend, seasonal, and remainder components. The decomposition of a time series  $y_t$ is written as $y_t = T_t + S_{t} + R_t$, where $T_t$ is the smoothed trend component, $S_t$ is the seasonal component and $R_t$ is a remainder component. The strength of trend is defined as:}
$$F_T = \max\left(0, 1 - \frac{\text{Var}(R_t)}{\text{Var}(T_t+R_t)}\right)$$
\textcolor{teal}{For strongly trended data, the seasonally adjusted data should have much more variation than the remainder component. Therefore Var($R_t$)/Var($T_t+R_t$) should be relatively small. But for data with little or no trend, the two variances should be approximately the same.}

@@

In addition to displaying the trend and seasonality features, we also visualize few time series at various levels of the aggregation. @fig-dataviz2 reveals different information such as trend, seasonality, and noise. For example, some series depict seasonality and trend, whereas some other series report low volume of attended incidents and entropy, making them more volatile and difficult to forecast. At the level on nature of incidents combined with categories of other levels, there are many series that contain zeros with low counts. As such, the data set represents a diverse set of daily time series patterns.

@@

**Naive:** We start with a simple forecasting approach, assuming that the future days will be similar to past days. We use the empirical distribution of the past daily attended incidents to create the forecast distribution of future attended incidents. \textcolor{teal}{We have chosen the naive method as a benchmark due to its widespread usage and simplicity, making it easily understandable for users. Forecasts serve as inputs for various decision-making systems that frequently employ simulations, wherein it is common to utilize the empirical distribution of demand as a forecast. Additionally, the naive method has shown surprisingly high accuracy. Hence, any forecasting approach that can offer superior results compared to the naive method would validate its practical use, otherwise there is no necessity for employing more complex methods.}

@@

\textcolor{teal}{In our study, we use an automated algorithm to determine the suitable configuration for the trend, seasonality, and error terms in each time series. Specifically, we utilize the `ETS()` function in the fable package of R, which employs statistical criteria like Akaike's Information Criterion (AIC) to identify the optimal model for each time series. Given the large number of time series we work with (1530), it is impractical to manually select the appropriate form for each component in every time series. Consequently, the automated algorithm selects the most fitting components based on the unique characteristics of each individual time series. As a result, a combination of additive or multiplicative forms for the components are employed, depending on the specific attributes of each time series.}

@@

\textcolor{teal}{Suppose the time series is denoted by $y_1,\dots,y_T$, then the Poisson GLM can be written as}

\begin{align*}
  y_t &\sim \text{Poisson}(\lambda_t) \\
  \text{where}\qquad
  \log(\lambda_t) &= \bm{x}_t'\bm{\beta},
\end{align*}

\textcolor{teal}{and $\bm{x}_t$ is a vector of covariates, $\beta$ is a vector of coefficients, and $\lambda_t$ is the parameter of Poisson distribution. In our model, these include cubic splines for the time trend, day-of-week dummy variables (from Monday to Sunday), Fourier terms to capture the yearly seasonality, dummy variables indicating public holidays (1 when is public holiday, 0 otherwise), school holidays (1 when is school holiday, 0 otherwise) and Christmas Day (1 when is Christmas Day, 0 otherwise) and New Year's Day (1 when is New Year's Day, 0 otherwise). The Fourier terms are as defined in} @hyndman2021forecasting \textcolor{teal}{(Section 7.4). This model takes account of weekly seasonality and annual seasonality. Monthly seasonality is exceedingly rare in time series data, and does not occur in ambulance demand. There is no reason, for example, for incidents to occur more at some times of the month than others.}

@@

\textcolor{teal}{The Poisson TSGLM is similar to GLM with an additional component accounting for serial correlation (i.e. autoregressive). The term serial dependence refers to situations where the ambulance demand at a given time point exhibits correlation with the demand at previous time points. Put simply, past values of the time series influence the current values, and various techniques can be employed to model this influence. TSGLM can be written as}

\begin{align*}
  y_t &\sim \text{Poisson}(\lambda_t) \\
  \text{where}\qquad
  \log(\lambda_t) &= (\bm{y}_{t-k}'+\bm{x}_t')\bm{\beta},
\end{align*}

\textcolor{teal}{${y}_{t-k}$ is a vector of k lagged values. The TSGLM model explicitly accounts for serial dependence by including lagged values (i.e. past values) of the ambulance demand in the model. This is important in EMS forecasting because it allows the model to capture patterns in the data that are dependent on the past values of the time series, which might not be captured via the predictor variables.}

\textcolor{teal}{We use the `tsglm()` function in the `tscount` package in R} [@JSSv082i05] \textcolor{teal}{to model the attended incidents. Again, the logarithmic link function is used to ensure that the parameter of Poisson distribution is always positive.}

\textcolor{teal}{Provided accidents occur independently, they will inherently follow a Poisson distribution} [@feller1991introduction, p156-158]. \textcolor{teal}{Hence, it is reasonable to assume a Poisson distribution in this context. To account for changes over time, we incorporate trend and seasonality covariates, as well as public holiday effects, allowing the mean of the Poisson distribution to vary. However, it is important to note that if there are additional factors influencing the mean of the Poisson distribution, which are not accounted for in our model, we might observe over-dispersion or under-dispersion in the data.}

**Ensemble method:** \textcolor{teal}{Finally, one effective strategy for improving forecast accuracy includes the simultaneous application of multiple forecasting methods on a given time series, followed by averaging the forecasts, rather than relying on separate forecasts generated by each individual method} [@clemen1989combining]. \textcolor{teal}{In this paper, we use an ensemble method that combines the forecasts generated from the Naive, ETS, GLM and TSGLM models using a simple average to form a mixture distribution} [@combinations].

\textcolor{teal}{To generate forecast probability distributions using above methods, we use a form of bootstrapping, described in} @panagiotelis2023probabilistic. \textcolor{teal}{This involves simulating 1000 future sample paths from each of the model, by bootstrapping the model residuals, taking into account the cross-sectional correlations between the different aggregated and disaggregated series. In this way, we can generate an empirical distribution of forecasts for each model. The ensemble forecast distribution is a simple mixture of these empirical distributions.}

\textcolor{teal}{It is important to emphasize that the aim of this study is not to provide an exhaustive compilation of forecasting models or promote a particular model class. Instead, we have developed a flexible framework that can accommodate any forecasting models. Our primary objective is to demonstrate its practicality and effectiveness in integrating base forecasts from any model and generating coherent forecasts within a hierarchical structure.}

@@

\textcolor{teal}{The error metrics provided below consider a forecasting horizon denoted by j, representing the number of time periods ahead we are predicting. In our study, this forecasting horizon ranges from 1 to 84 days, $j= 1,2,\dots, 84$.}

@@

\textcolor{teal}{Using of scale-independent measures, such as MASE and MSSE, enables more significant comparisons between time series at different levels and scales, as these measures are not influenced by the data's magnitude. This aspect holds particular importance in our study, as we work with time series at various levels of hierarchy. These time series show varying scales, resulting in different magnitudes of error. By employing scale-independent measures, we can meaningfully assess the forecast accuracy across the entire hierarchy, ensuring a more robust comparison.}

@@

\textcolor{teal}{Calibration refers to the statistical consistency between the distributional forecasts and the observations. It measures how well the predicted probabilities match the actual. On the other hand, sharpness refers to the concentration of the forecast distributions --- a sharp forecast distribution results in narrow prediction intervals, indicating high confidence in the forecast. A model is well-calibrated if the predicted probabilities match the actual, and it is sharp if it is confident in its predictions. The CRPS rewards sharpness and calibration by assigning lower scores to forecasts with sharper distributions, and to forecasts that are well-calibrated. Thus, it is a metric that combines both sharpness and miscalibration into a single score, making it a useful tool for evaluating the performance of probabilistic forecasts.}

\textcolor{teal}{CRPS can be considered an average of all possible Winkler scores} [@winkler1972decision;@hyndman2021forecasting, Section 5.9] \textcolor{teal}{or percentile scores} [@hyndman2021forecasting, section 5.9], \textcolor{teal}{and thus provides an evaluation of all possible prediction intervals or quantiles.} \textcolor{teal}{A specific prediction interval could be evaluated using a Winkler score. Certain situations may also require assessing accuracy for a particular quantile, such as lower (e.g 5\%) or higher (e.g. 95\%) quantiles. In such cases, a percentile score  becomes useful in meeting this specific requirement.}

>>>>

\textcolor{teal}{In this paper, the strength of trend and seasonality were calculated using the "STL" (Seasonal and Trend decomposition using Loess) decomposition method, as described by} @mstl. \textcolor{teal}{STL is a widely used and flexible method for decomposing time series data into trend, seasonal, and remainder components. The decomposition of a time series  $y_t$ is written as $y_t = T_t + S_{t} + R_t$, where $T_t$ is the smoothed trend component, $S_t$ is the seasonal component and $R_t$ is a remainder component. The strength of trend is defined as:}
$$F_T = \max\left(0, 1 - \frac{\text{Var}(R_t)}{\text{Var}(T_t+R_t)}\right)$$
\textcolor{teal}{For strongly trended data, the seasonally adjusted data should have much more variation than the remainder component. Therefore Var($R_t$)/Var($T_t+R_t$) should be relatively small. But for data with little or no trend, the two variances should be approximately the same.}

@@

In addition to displaying the trend and seasonality features, we also visualize a few time series at various levels of aggregation. @fig-dataviz2 reveals different information such as trend, seasonality, and noise. For example, some series depict seasonality and trend, whereas some other series report low volume of attended incidents and entropy, making them more volatile and difficult to forecast. At the level on nature of incidents combined with categories of other levels, there are many series that contain zeros with low counts. As such, the data set represents a diverse set of daily time series patterns.

@@

**Stationary:** We start with a simple forecasting approach, assuming that the future days will be similar to past days. We use the empirical distribution of the past daily attended incidents to create the forecast distribution of future attended incidents. \textcolor{teal}{We have chosen this "stationary" method as a benchmark due to its widespread usage and simplicity, making it easily understandable for users. Forecasts serve as inputs for various decision-making systems that frequently employ simulations, wherein it is common to utilize the empirical distribution of demand as a forecast. Additionally, the stationary method has shown surprisingly high accuracy. Hence, any forecasting approach that can offer superior results compared to the stationary method would validate its practical use, otherwise there is no necessity for employing more complex methods.}

@@

\textcolor{teal}{In our study, we use an automated algorithm to determine the suitable configuration for the trend, seasonality, and error terms in each time series. Specifically, we utilize the `ETS()` function in the fable package of R, which employs Akaike's Information Criterion (AIC) to identify the optimal model for each time series. Given the large number of time series we work with (1530), it is impractical to manually select the appropriate form for each component in every time series. Consequently, the automated algorithm selects the best model based on the unique characteristics of each individual time series. As a result, a combination of additive or multiplicative forms for the components are employed, depending on the specific attributes of each time series.}

@@

\textcolor{teal}{Suppose the time series is denoted by $y_1,\dots,y_T$, then the Poisson GLM can be written as}
\begin{align*}
  y_t &\sim \text{Poisson}(\lambda_t) \\
  \text{where}\qquad
  \log(\lambda_t) &= \bm{x}_t'\bm{\beta},
\end{align*}
\textcolor{teal}{and $\bm{x}_t$ is a vector of covariates, $\beta$ is a vector of coefficients, and $\lambda_t$ is the mean of the Poisson distribution. In our model, these include cubic splines for the time trend, day-of-week dummy variables (from Monday to Sunday), Fourier terms to capture the yearly seasonality, dummy variables indicating public holidays (1 when is public holiday, 0 otherwise), school holidays (1 when is school holiday, 0 otherwise) and Christmas Day (1 when is Christmas Day, 0 otherwise) and New Year's Day (1 when is New Year's Day, 0 otherwise). The Fourier terms are as defined in} @hyndman2021forecasting [Section 7.4] \textcolor{teal}{This model takes account of weekly seasonality and annual seasonality. Monthly seasonality is exceedingly rare in time series data, and does not occur in ambulance demand. There is no reason, for example, for incidents to occur more at some times of the month than others.}

@@

\textcolor{teal}{The Poisson TSGLM is similar to GLM with an additional autoregressive component accounting for serial correlation. The term serial dependence refers to situations where the ambulance demand at a given time point exhibits correlation with the demand at previous time points, after accounting for the exogenous covariates. Put simply, past values of the time series influence the current values, and various techniques can be employed to model this influence. TSGLM can be written as}
\begin{align*}
  y_t &\sim \text{Poisson}(\lambda_t) \\
  \text{where}\qquad
  \log(\lambda_t) &= (\bm{y}_{t-k}' , \bm{x}_t')\bm{\beta},
\end{align*}
\textcolor{teal}{and ${y}_{t-k}$ is a vector of $k$ lagged values. The TSGLM model explicitly accounts for serial dependence by including lagged values (i.e. past values) of the ambulance demand in the model. This is important in EMS forecasting because it allows the model to capture patterns in the data that are dependent on the past values of the time series, which might not be captured via the predictor variables.}

\textcolor{teal}{We use the `tsglm()` function in the `tscount` package in R} [@JSSv082i05] \textcolor{teal}{to model the attended incidents. Again, the logarithmic link function is used to ensure that the mean of the Poisson distribution is always positive.}

\textcolor{teal}{Provided accidents occur independently, they will inherently follow a Poisson distribution} [@feller1991introduction, p156--158]. \textcolor{teal}{Hence, it is reasonable to assume a Poisson distribution in this context. To account for changes over time, we incorporate trend and seasonality covariates, as well as public holiday effects, allowing the mean of the Poisson distribution to vary. However, it is important to note that if there are additional factors influencing the mean of the Poisson distribution, which are not accounted for in our model, we might observe over-dispersion or under-dispersion in the data.}

**Ensemble method:** \textcolor{teal}{Finally, one effective strategy for improving forecast accuracy includes the simultaneous application of multiple forecasting methods on a given time series, followed by combining the forecasts, rather than relying on separate forecasts generated by each individual method} [@clemen1989combining]. \textcolor{teal}{In this paper, we use an ensemble method that combines the forecasts generated from the Stationary, ETS, GLM and TSGLM models using a simple average to form a mixture distribution} [@combinations].

\textcolor{teal}{To generate forecast probability distributions using above methods, we use a form of bootstrapping, described in} @panagiotelis2023probabilistic. \textcolor{teal}{This involves simulating 1000 future sample paths from each of the models, by bootstrapping the model residuals, taking into account the cross-sectional correlations between the different aggregated and disaggregated series. In this way, we can generate an empirical distribution of forecasts for each model. The ensemble forecast distribution is a simple mixture of these empirical distributions.}

\textcolor{teal}{It is important to emphasize that the aim of this study is not to provide an exhaustive compilation of forecasting models, or to promote a particular model class. Instead, we have developed a flexible framework that can accommodate any forecasting models. Our primary objective is to demonstrate its practicality and effectiveness in integrating base forecasts from any model and generating coherent forecasts within a hierarchical structure.}

@@

\textcolor{teal}{The error metrics provided below consider a forecasting horizon denoted by $j$, representing the number of time periods ahead we are predicting. In our study, this forecasting horizon ranges from 1 to 84 days, $j= 1,2,\dots, 84$.}

@@

\textcolor{teal}{Using scale-independent measures, such as MASE and MSSE, enables more appropriate comparisons between time series at different levels and scales, as these measures are not influenced by the magnitude of the data. This is of particular importance in our study, as we work with time series at various levels of hierarchy, with varying scales, resulting in different magnitudes of error. By employing scale-independent measures, we can meaningfully assess the forecast accuracy across the entire hierarchy, ensuring a more robust comparison.}

@@

\textcolor{teal}{Calibration refers to the statistical consistency between the distributional forecasts and the observations. It measures how well the predicted probabilities match the observations. On the other hand, sharpness refers to the concentration of the forecast distributions --- a sharp forecast distribution results in narrow prediction intervals, indicating high confidence in the forecast. A model is well-calibrated if the predicted probabilities match the distribution of the observations, and it is sharp if it is confident in its predictions. The CRPS rewards sharpness and calibration by assigning lower scores to forecasts with sharper distributions, and to forecasts that are well-calibrated. Thus, it is a metric that combines both sharpness and miscalibration into a single score, making it a useful tool for evaluating the performance of probabilistic forecasts.}

\textcolor{teal}{CRPS can be considered an average of all possible Winkler scores} [@winkler1972decision;@hyndman2021forecasting, Section 5.9] \textcolor{teal}{or percentile scores} [@hyndman2021forecasting, Section 5.9], \textcolor{teal}{and thus provides an evaluation of all possible prediction intervals or quantiles.} \textcolor{teal}{A specific prediction interval could be evaluated using a Winkler score. Certain situations may also require assessing accuracy for a particular quantile, such as lower (e.g 5\%) or higher (e.g. 95\%) quantiles. In such cases, a percentile score becomes useful in meeting this specific requirement.}

### 2023-07-19 manuscript/04-htsgts.qmd
Minor rewording, typos and fixed some refs

Let $\bm{b}_t$ be a vector of $n_b$ _bottom-level_ time series at time $t$, and let $\bm{a}_t$ be a corresponding vector of $n_a = n-n_b$ aggregated time series, where
$$
  \bm{a}_t = \bm{A}\bm{b}_t,
$$
and $\bm{A}$ is the $n_a\times n_b$ "aggregation" matrix specifying how the bottom-level series $\bm{b}_t$ are to be aggregated to form $\bm{a}_t$. \textcolor{teal}{The aggregation matrix $A$ is determined by the structure of the hierarchy. It maps the bottom-level time series to the corresponding higher-level time series. The matrix $A$ is typically predefined based on the structure of the hierarchy, and it remains fixed throughout the forecasting process. For example, if there are two bottom-level series, and one aggregated series (equal to the sum of the two bottom-level series), then $A = \begin{bmatrix} 1 1 \end{bmatrix}$.
}

The full vector of time series is given by
$$
 \bm{y}_t = \begin{bmatrix}\bm{a}_t \\\bm{b}_t\end{bmatrix}.
$$
This leads to the $n\times n_b$ "summing" or "structural" matrix given by
$$
  \bm{S} = \begin{bmatrix}\bm{A} \\ \bm{I}_{n_b}\end{bmatrix}
$$
such that $\bm{y}_t = \bm{S}\bm{b}_t$.

\textcolor{teal}{The term "level bottom series" relates to the most disaggregated series within the hierarchical and grouped time series structure. For instance, in Table 2, each distinct combination of values in Control area (e.g. South \& East), Health board (e.g. CV), Priority (e.g. Green), and Nature of incident (e.g. Chest pain) corresponds to one individual time series. In the dataset at hand, there are 691 unique combinations, resulting in 691 bottom level time series. The "aggregate time series" describes how these bottom-level series are combined to create higher-level series. For instance, to obtain the incidents at the national level (i.e. all country level), the time series are aggregated across all Control areas, Health boards, Priorities, and Natures of incidents. Any desired aggregation level can be achieved based on the data structure, utilizing the bottom level series available.}

@@

Bottom-Up is a simple approach to generate coherent forecasts. It involves first creating the base forecasts for the bottom level series (i.e., the most disaggregated series). These forecasts are then aggregated to the upper levels which naturally results in coherent forecasts. The BU approach can capture the dynamics of the series at the bottom level, but these series may be noisy and difficult to forecast. The approach uses only the data at the most disaggregated level, and so does not utilize all the information available across the hierarchical and grouped structure.

@@

\textcolor{teal}{Ordinary Least Squares (OLS) is the simplest and most commonly used method for estimating the parameters in linear regression models. In this approach, the estimation of W is based on the assumption that all the errors have equal variance. Hence, W is simply defined as the identity matrix multiplied by a constant factor. The intuition behind OLS is that it minimizes the sum of squared residuals between the observed and predicted values of the dependent variable. The main weakness of this approach is that it does not take account of the different scales of the base time series; the aggregated series will usually have higher variance than the disaggregated series, simply because the values are larger, but OLS treats all series the same. A strength of the approach is that it is simple, and does not involve estimating a covariance matrix.}

\textcolor{teal}{Weighted Least Squares (WLS) is an extension of OLS where the variance of the errors is assumed to be heteroscedastic, i.e., different for each series. But it assumes that the errors of each series are uncorrelated with each other. In this approach, W is defined as a diagonal matrix with the variance of the errors on the diagonal. The intuition behind WLS is that it assigns higher weight to series with smaller error variance, and thereby takes into account the different scales of the base time series. The main weakness of this approach is that it ignores the relationships between series. A strength of WLS is that it is relatively easy to compute W as it is based only on error variances which are readily estimated.}

\textcolor{teal}{Minimum Trace (MinT) is a further generalization where W is defined as the covariance matrix of the base forecast errors. So it takes account of both the scale of each series, and the relationships between the series.} @WicEtAl2019 \textcolor{teal}{showed that this approach gives the optimal reconciled forecasts in the sense that the sum of the forecast variances is minimized. The main weakness of this approach is that it is difficult to estimate the full covariance matrix. In practice, we usually need to use a shrinkage estimate where the off-diagonal elements are shrunk towards zero.}

>>>>

Let $\bm{b}_t$ be a vector of $n_b$ _bottom-level_ time series at time $t$, and let $\bm{a}_t$ be a corresponding vector of $n_a = n-n_b$ aggregated time series, where
$$
  \bm{a}_t = \bm{A}\bm{b}_t,
$$
and $\bm{A}$ is the $n_a\times n_b$ "aggregation" matrix specifying how the bottom-level series $\bm{b}_t$ are to be aggregated to form $\bm{a}_t$. \textcolor{teal}{The aggregation matrix $\bm{A}$ is determined by the structure of the hierarchy. It maps the bottom-level time series to the corresponding higher-level time series. For example, if there are two bottom-level series, and one aggregated series (equal to the sum of the two bottom-level series), then $\bm{A} = \begin{bmatrix} 1 ~~ 1 \end{bmatrix}$.
}
The full vector of time series is given by
$$
 \bm{y}_t = \begin{bmatrix}\bm{a}_t \\\bm{b}_t\end{bmatrix}.
$$
This leads to the $n\times n_b$ "summing" or "structural" matrix given by
$$
  \bm{S} = \begin{bmatrix}\bm{A} \\ \bm{I}_{n_b}\end{bmatrix}
$$
such that $\bm{y}_t = \bm{S}\bm{b}_t$.

\textcolor{teal}{The term "bottom-level series" relates to the most disaggregated series within the hierarchical and grouped time series structure. For instance, in Table 2, each distinct combination of values in Control area (e.g. South \& East), Health board (e.g. CV), Priority (e.g. Green), and Nature of incident (e.g. Chest pain), corresponds to one individual time series. In the dataset at hand, there are 691 unique combinations, resulting in 691 bottom level time series. The "aggregate time series" describes how these bottom-level series are combined to create higher-level series. For instance, to obtain the incidents at the national level (i.e. all country level), the time series are aggregated across all Control areas, Health boards, Priorities, and Natures of incidents. Any desired aggregation level can be achieved based on the data structure, utilizing the bottom-level series available.}

@@

Bottom-Up is a simple approach to generate coherent forecasts. It involves first creating the base forecasts for the bottom-level series (i.e., the most disaggregated series). These forecasts are then aggregated to the upper levels which naturally results in coherent forecasts. The BU approach can capture the dynamics of the series at the bottom level, but these series may be noisy and difficult to forecast. The approach uses only the data at the most disaggregated level, and so does not utilize all the information available across the hierarchical and grouped structure.

@@

\textcolor{teal}{Ordinary Least Squares (OLS) is the simplest and most commonly used method for estimating the parameters in linear regression models. In this approach, the estimation of $\bm{W}$ is based on the assumption that all the errors have equal variance. Hence, $\bm{W}$ is simply defined as the identity matrix multiplied by a constant factor. The intuition behind OLS is that it minimizes the sum of squared residuals between the observed and predicted values of the dependent variable. The main weakness of this approach is that it does not take account of the different scales of the base time series; the aggregated series will usually have higher variance than the disaggregated series, simply because the values are larger, but OLS treats all series the same. A strength of the approach is that it is simple, and does not involve estimating a covariance matrix.}

\textcolor{teal}{Weighted Least Squares (WLS) is an extension of OLS where the variance of the errors is assumed to be heteroscedastic, i.e., different for each series. But it assumes that the errors of each series are uncorrelated with each other. In this approach, $\bm{W}$ is defined as a diagonal matrix with the variance of the errors on the diagonal. The intuition behind WLS is that it assigns higher weight to series with smaller error variance, and thereby takes into account the different scales of the base time series. The main weakness of this approach is that it ignores the relationships between series. A strength of WLS is that it is relatively easy to compute $\bm{W}$ as it is based only on error variances which are readily estimated.}

\textcolor{teal}{Minimum Trace (MinT) is a further generalization where $\bm{W}$ is defined as the covariance matrix of the base forecast errors. So it takes account of both the scale of each series, and the relationships between the series.} @WicEtAl2019 \textcolor{teal}{showed that this approach gives the optimal reconciled forecasts in the sense that the sum of the forecast variances is minimized. The main weakness of this approach is that it is difficult to estimate the full covariance matrix. In practice, we usually need to use a shrinkage estimate where the off-diagonal elements are shrunk towards zero.}
